---
title: "Wild Boar Tolerance Study"
subtitle: "2.2 Robustness Checks | 3.4 Multi-Group Analysis"
author: "Isha"
date: "`r Sys.Date()`"
output:
  ioslides_presentation:
    widescreen: true
    smaller: false
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = FALSE,
  warning   = FALSE,
  message   = FALSE,
  fig.align = "center",
  fig.width = 9,
  fig.height = 5
)
```

```{r libraries}
library(readxl)
library(tidyverse)
library(seminr)
library(ggplot2)
library(dplyr)
library(knitr)
library(kableExtra)
```

```{r data-setup}
# ── Load raw data (keep CE0 unscaled for group splitting) ────────────────────
Data_all <- read_excel("3_Data.xlsx")

# ── Save CE0 grouping BEFORE scaling ─────────────────────────────────────────
CE0_group <- as.numeric(as.character(Data_all$CE0))

# ── Select, clean, scale (same as Mengxi's pipeline) ─────────────────────────
Data_allinput <- Data_all %>%
  select(
    "CP_WB1","CP_WB2","CP_WB3","CP_WB4",
    "CP_A1","CP_A2","CP_A3",
    "TC1_DamagedArea","TC2_EconomicLoss",
    "IC1","IC2_1","IC2_2","IC2_3","IC2_DescriptiveAttitude",
    "IB","Tol1_5","Tol2_1","Tol3_1","Tol4_5",
    "PE","CE0","CE1","CE2","CA1","CA2","CA3","PS1","PS2",
    "Q4_Gender","Q5_Age","Q6_Education","Q8_AnnualIncome",
    "Q14_HouseholdAsset","Q14_CropAsset"
  ) %>%
  mutate(across(everything(), ~as.numeric(as.character(.)))) %>%
  scale() %>%
  as.data.frame()

# ── Split groups using unscaled CE0 (before scaling) ─────────────────────────
Data_comp   <- Data_allinput[CE0_group == 1, ]   # WITH compensation
Data_nocomp <- Data_allinput[CE0_group == 0, ]   # WITHOUT compensation

n_comp   <- nrow(Data_comp)
n_nocomp <- nrow(Data_nocomp)
```

```{r helper-functions}
# ── Helper: extract beta + bootstrap CI for one path ─────────────────────────
get_path_info <- function(boot_summary, from, to) {
  # seminr labels paths as "FROM  ->  TO" (two spaces each side of arrow)
  row_label <- paste0(from, "  ->  ", to)
  tryCatch({
    b  <- boot_summary$bootstrapped_paths[row_label, "Original Est."]
    lo <- boot_summary$bootstrapped_paths[row_label, "2.5% CI"]
    hi <- boot_summary$bootstrapped_paths[row_label, "97.5% CI"]
    data.frame(beta = b, ci_low = lo, ci_high = hi)
  }, error = function(e) data.frame(beta = NA, ci_low = NA, ci_high = NA))
}

# ── Helper: extract R² for Tolerance ─────────────────────────────────────────
get_r2 <- function(pls_summary) {
  tryCatch(pls_summary$paths["Tolerance", "R^2"], error = function(e) NA)
}
```

```{r baseline-model}
# ── Baseline Measurement Model (M0.1 — Mengxi's refined model) ───────────────
# RULE: single indicator  → single_item()
#       multiple indicators, formative → composite(..., weights = mode_B)
#       multiple indicators, reflective → reflective()

mm_base <- constructs(
  # Multi-item formative (mode B)
  composite("ConflictExp_WB",   c("CP_WB1","CP_WB2","CP_WB4"),          weights = mode_B),
  composite("ConflictExp_A",    c("CP_A1","CP_A2","CP_A3"),             weights = mode_B),
  composite("Policy_Support",   c("PS1","PS2"),                          weights = mode_B),
  composite("Tangible_Costs",   c("TC1_DamagedArea","TC2_EconomicLoss"), weights = mode_B),
  composite("Intangible_Costs", c("IC1","IC2_1","IC2_2"),               weights = mode_B),

  # Single-item constructs
reflective("Prevention_Effectiveness",  "PE"),
reflective("Compensation_Experience",   "CE0"),
reflective("Compensation_Anticipation", "CA3"),
reflective("Intangible_Benefits",       "IB"),
  # Multi-item reflective (mode A)
  reflective("Gender",         c("Q4_Gender")),
  reflective("Age",            c("Q5_Age")),
  reflective("Education",      c("Q6_Education")),
  reflective("AnnualIncome",   c("Q8_AnnualIncome")),
  reflective("HouseholdAsset", c("Q14_CropAsset")),
  reflective("Tolerance",      c("Tol1_5","Tol2_1","Tol4_5"))
)

# ── Baseline Structural Model ─────────────────────────────────────────────────
sm_base <- relationships(
  paths(from = c("ConflictExp_WB","ConflictExp_A"),
        to   = c("Prevention_Effectiveness","Compensation_Experience",
                 "Compensation_Anticipation","Policy_Support")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Experience","Compensation_Anticipation","Policy_Support"),
        to   = c("Tangible_Costs","Intangible_Costs","Intangible_Benefits")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Experience","Compensation_Anticipation","Policy_Support",
                 "Tangible_Costs","Intangible_Costs","Intangible_Benefits",
                 "Gender","Age","Education","AnnualIncome","HouseholdAsset"),
        to   = "Tolerance")
)

# ── Estimate + bootstrap baseline ────────────────────────────────────────────
pls_base      <- estimate_pls(Data_allinput, mm_base, sm_base,
                               inner_weights = path_weighting)
sum_base      <- summary(pls_base)
boot_base     <- bootstrap_model(pls_base, nboot = 1000, seed = 42)
sum_boot_base <- summary(boot_base, alpha = 0.05)
```


# Section 2.2 {.section-header}
## Robustness Checks & Vibration of Effects


## Why Robustness Checks?

> "The aim is **not** to search for significant results, but to examine how sensitive the main findings are to different reasonable analytical choices."
> — StaBLab Notes, Section 2.2

**We test whether Compensation Experience → Tolerance stays stable when we:**

- Drop socio-demographic control variables
- Drop Tangible Costs (weak predictor)
- Drop Policy Support (HTMT concern from Section 3.2)
- Use IC1 only for Intangible Costs (conservative specification)
- Use all 4 Tolerance indicators


## Model Specifications Tested

```{r specs-table}
data.frame(
  Model = c("M0.1 (Base)","M_noSocio","M_noTangible",
            "M_noPS","M_IC1only","M_TolFull"),
  Change = c(
    "Mengxi's refined baseline — all predictors",
    "Remove Gender, Age, Education, Income, Asset",
    "Remove Tangible Costs",
    "Remove Policy Support (HTMT = 1.112 issue)",
    "Intangible Costs = IC1 only",
    "Tolerance = Tol1_5, Tol2_1, Tol3_1, Tol4_5"
  ),
  Rationale = c(
    "Reference model",
    "Check if demographics inflate compensation effect",
    "Test if tangible costs confound the relationship",
    "Address discriminant validity concern",
    "Most conservative IC specification",
    "Alternative tolerance operationalisation"
  )
) %>%
  kable(col.names = c("Model","Specification","Rationale"), align = "lll") %>%
  kable_styling(font_size = 13, full_width = TRUE) %>%
  row_spec(1, bold = TRUE, background = "#f0f4ff")
```


```{r alternative-models}

# ── M_noSocio: drop all socio-demographic controls ───────────────────────────
mm_noSocio <- constructs(
  composite("ConflictExp_WB",   c("CP_WB1","CP_WB2","CP_WB4"),          weights = mode_B),
  composite("ConflictExp_A",    c("CP_A1","CP_A2","CP_A3"),             weights = mode_B),
  composite("Policy_Support",   c("PS1","PS2"),                          weights = mode_B),
  composite("Tangible_Costs",   c("TC1_DamagedArea","TC2_EconomicLoss"), weights = mode_B),
  composite("Intangible_Costs", c("IC1","IC2_1","IC2_2"),               weights = mode_B),
  reflective("Prevention_Effectiveness",  "PE"),
  reflective("Compensation_Experience",   "CE0"),
  reflective("Compensation_Anticipation", "CA3"),
  reflective("Intangible_Benefits",       "IB"),
  reflective("Tolerance", c("Tol1_5","Tol2_1","Tol4_5"))
)

sm_noSocio <- relationships(
  paths(from = c("ConflictExp_WB","ConflictExp_A"),
        to   = c("Prevention_Effectiveness","Compensation_Experience",
                 "Compensation_Anticipation","Policy_Support")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Experience","Compensation_Anticipation","Policy_Support"),
        to   = c("Tangible_Costs","Intangible_Costs","Intangible_Benefits")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Experience","Compensation_Anticipation","Policy_Support",
                 "Tangible_Costs","Intangible_Costs","Intangible_Benefits"),
        to   = "Tolerance")
)

pls_noSocio      <- estimate_pls(Data_allinput, mm_noSocio, sm_noSocio,
                                  inner_weights = path_weighting)
boot_noSocio     <- bootstrap_model(pls_noSocio, nboot = 1000, seed = 42)
sum_boot_noSocio <- summary(boot_noSocio, alpha = 0.05)


# ── M_noTangible: drop Tangible Costs ────────────────────────────────────────
mm_noTang <- constructs(
  composite("ConflictExp_WB",   c("CP_WB1","CP_WB2","CP_WB4"), weights = mode_B),
  composite("ConflictExp_A",    c("CP_A1","CP_A2","CP_A3"),    weights = mode_B),
  composite("Policy_Support",   c("PS1","PS2"),                 weights = mode_B),
  composite("Intangible_Costs", c("IC1","IC2_1","IC2_2"),      weights = mode_B),
  reflective("Prevention_Effectiveness",  "PE"),
  reflective("Compensation_Experience",   "CE0"),
  reflective("Compensation_Anticipation", "CA3"),
  reflective("Intangible_Benefits",       "IB"),
  reflective("Gender",         c("Q4_Gender")),
  reflective("Age",            c("Q5_Age")),
  reflective("Education",      c("Q6_Education")),
  reflective("AnnualIncome",   c("Q8_AnnualIncome")),
  reflective("HouseholdAsset", c("Q14_CropAsset")),
  reflective("Tolerance",      c("Tol1_5","Tol2_1","Tol4_5"))
)

sm_noTang <- relationships(
  paths(from = c("ConflictExp_WB","ConflictExp_A"),
        to   = c("Prevention_Effectiveness","Compensation_Experience",
                 "Compensation_Anticipation","Policy_Support")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Experience","Compensation_Anticipation","Policy_Support"),
        to   = c("Intangible_Costs","Intangible_Benefits")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Experience","Compensation_Anticipation","Policy_Support",
                 "Intangible_Costs","Intangible_Benefits",
                 "Gender","Age","Education","AnnualIncome","HouseholdAsset"),
        to   = "Tolerance")
)

pls_noTang      <- estimate_pls(Data_allinput, mm_noTang, sm_noTang,
                                 inner_weights = path_weighting)
boot_noTang     <- bootstrap_model(pls_noTang, nboot = 1000, seed = 42)
sum_boot_noTang <- summary(boot_noTang, alpha = 0.05)


# ── M_noPS: drop Policy Support ──────────────────────────────────────────────
mm_noPS <- constructs(
  composite("ConflictExp_WB",   c("CP_WB1","CP_WB2","CP_WB4"),          weights = mode_B),
  composite("ConflictExp_A",    c("CP_A1","CP_A2","CP_A3"),             weights = mode_B),
  composite("Tangible_Costs",   c("TC1_DamagedArea","TC2_EconomicLoss"), weights = mode_B),
  composite("Intangible_Costs", c("IC1","IC2_1","IC2_2"),               weights = mode_B),
  reflective("Prevention_Effectiveness",  "PE"),
  reflective("Compensation_Experience",   "CE0"),
  reflective("Compensation_Anticipation", "CA3"),
  reflective("Intangible_Benefits",       "IB"),
  reflective("Gender",         c("Q4_Gender")),
  reflective("Age",            c("Q5_Age")),
  reflective("Education",      c("Q6_Education")),
  reflective("AnnualIncome",   c("Q8_AnnualIncome")),
  reflective("HouseholdAsset", c("Q14_CropAsset")),
  reflective("Tolerance",      c("Tol1_5","Tol2_1","Tol4_5"))
)

sm_noPS <- relationships(
  paths(from = c("ConflictExp_WB","ConflictExp_A"),
        to   = c("Prevention_Effectiveness","Compensation_Experience",
                 "Compensation_Anticipation")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Experience","Compensation_Anticipation"),
        to   = c("Tangible_Costs","Intangible_Costs","Intangible_Benefits")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Experience","Compensation_Anticipation",
                 "Tangible_Costs","Intangible_Costs","Intangible_Benefits",
                 "Gender","Age","Education","AnnualIncome","HouseholdAsset"),
        to   = "Tolerance")
)

pls_noPS      <- estimate_pls(Data_allinput, mm_noPS, sm_noPS,
                               inner_weights = path_weighting)
boot_noPS     <- bootstrap_model(pls_noPS, nboot = 1000, seed = 42)
sum_boot_noPS <- summary(boot_noPS, alpha = 0.05)


# ── M_IC1only: Intangible Costs = IC1 only (single item) ─────────────────────
mm_IC1 <- constructs(
  composite("ConflictExp_WB",   c("CP_WB1","CP_WB2","CP_WB4"),          weights = mode_B),
  composite("ConflictExp_A",    c("CP_A1","CP_A2","CP_A3"),             weights = mode_B),
  composite("Policy_Support",   c("PS1","PS2"),                          weights = mode_B),
  composite("Tangible_Costs",   c("TC1_DamagedArea","TC2_EconomicLoss"), weights = mode_B),
  reflective("Prevention_Effectiveness",  "PE"),
  reflective("Compensation_Experience",   "CE0"),
  reflective("Compensation_Anticipation", "CA3"),
  reflective("Intangible_Costs",          "IC1"),
  reflective("Intangible_Benefits",       "IB"),
  reflective("Gender",         c("Q4_Gender")),
  reflective("Age",            c("Q5_Age")),
  reflective("Education",      c("Q6_Education")),
  reflective("AnnualIncome",   c("Q8_AnnualIncome")),
  reflective("HouseholdAsset", c("Q14_CropAsset")),
  reflective("Tolerance",      c("Tol1_5","Tol2_1","Tol4_5"))
)

pls_IC1      <- estimate_pls(Data_allinput, mm_IC1, sm_base,
                              inner_weights = path_weighting)
boot_IC1     <- bootstrap_model(pls_IC1, nboot = 1000, seed = 42)
sum_boot_IC1 <- summary(boot_IC1, alpha = 0.05)


# ── M_TolFull: Tolerance with all 4 items ────────────────────────────────────
mm_TolFull <- constructs(
  composite("ConflictExp_WB",   c("CP_WB1","CP_WB2","CP_WB4"),          weights = mode_B),
  composite("ConflictExp_A",    c("CP_A1","CP_A2","CP_A3"),             weights = mode_B),
  composite("Policy_Support",   c("PS1","PS2"),                          weights = mode_B),
  composite("Tangible_Costs",   c("TC1_DamagedArea","TC2_EconomicLoss"), weights = mode_B),
  composite("Intangible_Costs", c("IC1","IC2_1","IC2_2"),               weights = mode_B),
  reflective("Prevention_Effectiveness",  "PE"),
  reflective("Compensation_Experience",   "CE0"),
  reflective("Compensation_Anticipation", "CA3"),
  reflective("Intangible_Benefits",       "IB"),
  reflective("Gender",         c("Q4_Gender")),
  reflective("Age",            c("Q5_Age")),
  reflective("Education",      c("Q6_Education")),
  reflective("AnnualIncome",   c("Q8_AnnualIncome")),
  reflective("HouseholdAsset", c("Q14_CropAsset")),
  reflective("Tolerance",      c("Tol1_5","Tol2_1","Tol3_1","Tol4_5"))
)

sm_TolFull <- relationships(
  paths(from = c("ConflictExp_WB","ConflictExp_A"),
        to   = c("Prevention_Effectiveness","Compensation_Experience",
                 "Compensation_Anticipation","Policy_Support")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Experience","Compensation_Anticipation","Policy_Support"),
        to   = c("Tangible_Costs","Intangible_Costs","Intangible_Benefits")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Experience","Compensation_Anticipation","Policy_Support",
                 "Tangible_Costs","Intangible_Costs","Intangible_Benefits",
                 "Gender","Age","Education","AnnualIncome","HouseholdAsset"),
        to   = "Tolerance")
)

pls_TolFull      <- estimate_pls(Data_allinput, mm_TolFull, sm_TolFull,
                                  inner_weights = path_weighting)
boot_TolFull     <- bootstrap_model(pls_TolFull, nboot = 1000, seed = 42)
sum_boot_TolFull <- summary(boot_TolFull, alpha = 0.05)


# ── Compile robustness results ────────────────────────────────────────────────
from_var <- "Compensation_Experience"
to_var   <- "Tolerance"

robustness_results <- bind_rows(
  data.frame(Model = "M0.1 (Base)",  get_path_info(sum_boot_base,     from_var, to_var)),
  data.frame(Model = "M_noSocio",    get_path_info(sum_boot_noSocio,  from_var, to_var)),
  data.frame(Model = "M_noTangible", get_path_info(sum_boot_noTang,   from_var, to_var)),
  data.frame(Model = "M_noPS",       get_path_info(sum_boot_noPS,     from_var, to_var)),
  data.frame(Model = "M_IC1only",    get_path_info(sum_boot_IC1,      from_var, to_var)),
  data.frame(Model = "M_TolFull",    get_path_info(sum_boot_TolFull,  from_var, to_var))
)

robustness_results$Model <- factor(robustness_results$Model,
                                    levels = rev(robustness_results$Model))

# ── R² across specs ───────────────────────────────────────────────────────────
r2_results <- data.frame(
  Model = c("M0.1 (Base)","M_noSocio","M_noTangible",
            "M_noPS","M_IC1only","M_TolFull"),
  R2    = round(c(
    get_r2(sum_base),
    get_r2(summary(pls_noSocio)),
    get_r2(summary(pls_noTang)),
    get_r2(summary(pls_noPS)),
    get_r2(summary(pls_IC1)),
    get_r2(summary(pls_TolFull))
  ), 4)
)
r2_results$Model <- factor(r2_results$Model, levels = r2_results$Model)
```


## Vibration of Effects: Compensation Experience → Tolerance

```{r vibration-plot, fig.height=5.5}
ggplot(robustness_results, aes(x = beta, y = Model)) +
  geom_vline(xintercept = 0, linetype = "dashed",
             color = "grey50", linewidth = 0.7) +
 geom_errorbar(aes(xmin = ci_low, xmax = ci_high),
              width = 0.25, color = "#4a7ab5", linewidth = 0.9,
              orientation = "y") +
  geom_point(aes(color = beta < 0), size = 4.5) +
  scale_color_manual(
    values = c("TRUE"  = "#c0392b", "FALSE" = "#27ae60"),
    labels = c("TRUE"  = "Negative (expected)", "FALSE" = "Positive"),
    name   = "Direction"
  ) +
  geom_text(aes(label = round(beta, 3)),
            hjust = -0.4, size = 3.6, color = "grey25") +
  labs(
    title    = "Vibration of Effects: Compensation Experience → Tolerance",
    subtitle = "Path coefficients (β) with 95% bootstrap CIs across 6 model specifications",
    x        = "Standardised Path Coefficient (β)",
    y        = NULL
  ) +
  xlim(
    min(robustness_results$ci_low,  na.rm = TRUE) - 0.05,
    max(robustness_results$ci_high, na.rm = TRUE) + 0.15
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title       = element_text(face = "bold", size = 14),
    plot.subtitle    = element_text(color = "grey40", size = 11),
    legend.position  = "bottom",
    panel.grid.minor = element_blank()
  )
```


## R² Stability Across Specifications

```{r r2-plot, fig.height=4.5}
# Step 1: recreate r2_results with the fixed function
r2_results <- data.frame(
  Model = c("M0.1 (Base)","M_noSocio","M_noTangible",
            "M_noPS","M_IC1only","M_TolFull"),
  R2    = round(c(
    get_r2(sum_base),
    get_r2(summary(pls_noSocio)),
    get_r2(summary(pls_noTang)),
    get_r2(summary(pls_noPS)),
    get_r2(summary(pls_IC1)),
    get_r2(summary(pls_TolFull))
  ), 4)
)
r2_results$Model <- factor(r2_results$Model, levels = r2_results$Model)

# Step 2: check it has real values before plotting
print(r2_results)

# Step 3: then run the ggplot code
ggplot(r2_results, aes(x = Model, y = R2, fill = Model)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  geom_text(aes(label = round(R2, 3)),
            vjust = -0.5, size = 4, fontface = "bold") +
  geom_hline(yintercept = r2_results$R2[1], linetype = "dashed",
             color = "#c0392b", linewidth = 0.8) +
  annotate("text", x = 0.6, y = r2_results$R2[1] + 0.005,
           label = "Baseline R²", color = "#c0392b", hjust = 0, size = 3.5) +
  scale_fill_brewer(palette = "Blues") +
  scale_y_continuous(limits = c(0, max(r2_results$R2, na.rm = TRUE) + 0.05)) +
  labs(
    title    = "R² for Tolerance Across Specifications",
    subtitle = "Model explanatory power remains stable across analytical choices",
    x = NULL, y = "R²"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title       = element_text(face = "bold", size = 14),
    plot.subtitle    = element_text(color = "grey40"),
    axis.text.x      = element_text(angle = 25, hjust = 1),
    panel.grid.minor = element_blank()
  )
```


## Section 2.2 Key Takeaways

**Finding: The negative effect of Compensation Experience → Tolerance is robust.**

- Direction of β is **consistent across all 6 specifications**
- Magnitude stays within a **narrow range** regardless of which controls/indicators are used
- R² is **stable** — the model is not over-reliant on any single analytical choice
- This rules out **p-hacking** — the result is not produced by selective model building

> **Conclusion:** The negative association between compensation experience and tolerance is a genuine, replicable finding — not an artefact of the chosen model specification.


# Section 3.4 {.section-header}
## Multi-Group Analysis (MGA)


## Research Question

**Do structural relationships differ between:**

- 🟦 Residents **WITH** compensation experience (`CE0 = 1`)
- 🟥 Residents **WITHOUT** compensation experience (`CE0 = 0`)

**Method:** Permutation-based MGA (n = 1,000 permutations)

**Two MGA versions are compared:**

- **MGA 1:** Full model including socio-demographic controls
- **MGA 2:** Parsimonious model excluding socio-demographic controls — tests whether group differences are driven by demographics or core structural paths


## Sample Sizes per Group

```{r sample-table}
data.frame(
  Group      = c("With Compensation (CE0 = 1)",
                 "Without Compensation (CE0 = 0)",
                 "Total"),
  N          = c(n_comp, n_nocomp, n_comp + n_nocomp),
  Percentage = paste0(round(c(n_comp, n_nocomp, n_comp + n_nocomp) /
                              (n_comp + n_nocomp) * 100, 1), "%")
) %>%
  kable(col.names = c("Group","n","%"), align = "lrr") %>%
  kable_styling(font_size = 15, full_width = FALSE) %>%
  row_spec(1, background = "#dce9f7") %>%
  row_spec(2, background = "#fde8e8") %>%
  row_spec(3, bold = TRUE)
```

> ⚠️ **Note:** Unequal group sizes — permutation-based MGA is the appropriate test as it does not assume equal sample sizes or multivariate normality.


```{r mga-estimation}
# ── MGA 1: Full model (with socio) ───────────────────────────────────────────
mm_mga <- constructs(
  composite("ConflictExp_WB",   c("CP_WB1","CP_WB2","CP_WB4"),          weights = mode_B),
  composite("ConflictExp_A",    c("CP_A1","CP_A2","CP_A3"),             weights = mode_B),
  composite("Policy_Support",   c("PS1","PS2"),                          weights = mode_B),
  composite("Tangible_Costs",   c("TC1_DamagedArea","TC2_EconomicLoss"), weights = mode_B),
  composite("Intangible_Costs", c("IC1","IC2_1","IC2_2"),               weights = mode_B),
  reflective("Prevention_Effectiveness",  "PE"),
  reflective("Compensation_Anticipation", "CA3"),
  reflective("Intangible_Benefits",       "IB"),
  reflective("Gender",         c("Q4_Gender")),
  reflective("Age",            c("Q5_Age")),
  reflective("Education",      c("Q6_Education")),
  reflective("AnnualIncome",   c("Q8_AnnualIncome")),
  reflective("HouseholdAsset", c("Q14_CropAsset")),
  reflective("Tolerance",      c("Tol1_5","Tol2_1","Tol4_5"))
)

sm_mga <- relationships(
  paths(from = c("ConflictExp_WB","ConflictExp_A"),
        to   = c("Prevention_Effectiveness","Compensation_Anticipation","Policy_Support")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Anticipation","Policy_Support"),
        to   = c("Tangible_Costs","Intangible_Costs","Intangible_Benefits")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Anticipation","Policy_Support",
                 "Tangible_Costs","Intangible_Costs","Intangible_Benefits",
                 "Gender","Age","Education","AnnualIncome","HouseholdAsset"),
        to   = "Tolerance")
)

# ── MGA 2: Parsimonious model (no socio, IC1 only, CP_A1 only) ───────────────
mm_mga2 <- constructs(
  composite("ConflictExp_WB",            c("CP_WB1","CP_WB2","CP_WB4"),          weights = mode_B),
  composite("ConflictExp_A",             single_item("CP_A1")),
  composite("Prevention_Effectiveness",  single_item("PE")),
  composite("Compensation_Anticipation", single_item("CA3")),
  composite("Policy_Support",            c("PS1","PS2"),                          weights = mode_B),
  composite("Tangible_Costs",            c("TC1_DamagedArea","TC2_EconomicLoss"), weights = mode_B),
  composite("Intangible_Costs",          single_item("IC1")),
  reflective("Intangible_Benefits",      single_item("IB")),
  reflective("Tolerance",                c("Tol1_5","Tol2_1","Tol4_5"))
)

sm_mga2 <- relationships(
  paths(from = c("ConflictExp_WB","ConflictExp_A"),
        to   = c("Prevention_Effectiveness","Compensation_Anticipation","Policy_Support")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Anticipation","Policy_Support"),
        to   = c("Tangible_Costs","Intangible_Costs","Intangible_Benefits")),
  paths(from = c("ConflictExp_WB","ConflictExp_A","Prevention_Effectiveness",
                 "Compensation_Anticipation","Policy_Support",
                 "Tangible_Costs","Intangible_Costs","Intangible_Benefits"),
        to   = "Tolerance")
)

# ── Estimate per group — MGA 1 ────────────────────────────────────────────────
pls_comp   <- estimate_pls(Data_comp,   mm_mga,  sm_mga,  inner_weights = path_weighting)
pls_nocomp <- estimate_pls(Data_nocomp, mm_mga,  sm_mga,  inner_weights = path_weighting)

# ── Estimate per group — MGA 2 ────────────────────────────────────────────────
pls_comp2   <- estimate_pls(Data_comp,   mm_mga2, sm_mga2, inner_weights = path_weighting)
pls_nocomp2 <- estimate_pls(Data_nocomp, mm_mga2, sm_mga2, inner_weights = path_weighting)

# ── Define predictors ─────────────────────────────────────────────────────────
predictors_to_tol  <- rownames(pls_comp$path_coef)[!rownames(pls_comp$path_coef)  %in% "Tolerance"]
predictors_to_tol2 <- rownames(pls_comp2$path_coef)[!rownames(pls_comp2$path_coef) %in% "Tolerance"]

# ── Bootstrap ─────────────────────────────────────────────────────────────────
set.seed(123)
boot_comp      <- bootstrap_model(pls_comp,   nboot = 1000)
boot_nocomp    <- bootstrap_model(pls_nocomp, nboot = 1000)
boot_comp2     <- bootstrap_model(pls_comp2,  nboot = 1000)
boot_nocomp2   <- bootstrap_model(pls_nocomp2,nboot = 1000)

boot_comp_sum   <- summary(boot_comp,    alpha = 0.05)
boot_nocomp_sum <- summary(boot_nocomp,  alpha = 0.05)
boot_comp_sum2  <- summary(boot_comp2,   alpha = 0.05)
boot_nocomp_sum2<- summary(boot_nocomp2, alpha = 0.05)

# ── Permutation MGA helper ────────────────────────────────────────────────────
run_permutation_mga <- function(pls_c, pls_n, mm, sm, predictors, n_c, n_n) {
  obs_c    <- pls_c$path_coef[predictors, "Tolerance"]
  obs_n    <- pls_n$path_coef[predictors, "Tolerance"]
  obs_diff <- obs_c - obs_n

  Data_comb  <- rbind(Data_comp, Data_nocomp)
  grp_labels <- c(rep(1, n_c), rep(0, n_n))

  set.seed(42)
  perm_diffs <- replicate(1000, {
    pl <- sample(grp_labels)
    dc <- Data_comb[pl == 1, ]
    dn <- Data_comb[pl == 0, ]
    mc <- tryCatch(estimate_pls(dc, mm, sm, inner_weights = path_weighting), error = function(e) NULL)
    mn <- tryCatch(estimate_pls(dn, mm, sm, inner_weights = path_weighting), error = function(e) NULL)
    if (is.null(mc) | is.null(mn)) return(rep(NA, length(predictors)))
    mc$path_coef[predictors, "Tolerance"] - mn$path_coef[predictors, "Tolerance"]
  })

  p_vals <- sapply(seq_along(predictors), function(i) {
    nd <- na.omit(perm_diffs[i, ])
    mean(abs(nd) >= abs(obs_diff[i]))
  })

  data.frame(
    Predictor   = predictors,
    Beta_comp   = round(obs_c,    3),
    Beta_nocomp = round(obs_n,    3),
    Delta       = round(obs_diff, 3),
    p_value     = round(p_vals,   3),
    Significant = ifelse(p_vals < 0.05, "Yes *", "No")
  )
}

# ── Run both MGAs ─────────────────────────────────────────────────────────────
mga_df  <- run_permutation_mga(pls_comp,  pls_nocomp,  mm_mga,  sm_mga,
                                predictors_to_tol,  n_comp, n_nocomp)
mga_df2 <- run_permutation_mga(pls_comp2, pls_nocomp2, mm_mga2, sm_mga2,
                                predictors_to_tol2, n_comp, n_nocomp)

# ── Plot data ─────────────────────────────────────────────────────────────────
make_plot_df <- function(mga_df, predictors) {
  data.frame(
    Predictor    = predictors,
    With_Comp    = mga_df$Beta_comp,
    Without_Comp = mga_df$Beta_nocomp
  ) %>%
    pivot_longer(cols = c(With_Comp, Without_Comp),
                 names_to = "Group", values_to = "Beta") %>%
    mutate(
      Group     = recode(Group,
                         "With_Comp"    = "With Compensation",
                         "Without_Comp" = "Without Compensation"),
      Predictor = str_replace_all(Predictor, "_", " ")
    )
}

plot_df  <- make_plot_df(mga_df,  predictors_to_tol)
plot_df2 <- make_plot_df(mga_df2, predictors_to_tol2)

diff_df  <- data.frame(Predictor = str_replace_all(predictors_to_tol,  "_", " "),
                        Delta = mga_df$Delta,  p_value = mga_df$p_value)
diff_df2 <- data.frame(Predictor = str_replace_all(predictors_to_tol2, "_", " "),
                        Delta = mga_df2$Delta, p_value = mga_df2$p_value)

# ── Bootstrap CI helper ───────────────────────────────────────────────────────
get_boot_paths <- function(boot_sum, group_label) {
  df <- as.data.frame(boot_sum$bootstrapped_paths)
  df$Path <- rownames(df)
  df %>%
    filter(grepl("->  Tolerance", Path)) %>%
    mutate(
      Predictor = str_replace(Path, "  ->  Tolerance", ""),
      Predictor = str_replace_all(Predictor, "_", " "),
      Group     = group_label
    ) %>%
    select(Predictor, Group,
           Beta  = `Original Est.`,
           Lower = `2.5% CI`,
           Upper = `97.5% CI`)
}

ci_df  <- bind_rows(get_boot_paths(boot_comp_sum,   "With Compensation"),
                    get_boot_paths(boot_nocomp_sum,  "Without Compensation"))
ci_df2 <- bind_rows(get_boot_paths(boot_comp_sum2,  "With Compensation"),
                    get_boot_paths(boot_nocomp_sum2, "Without Compensation"))
```


## MGA 1 (Full Model) — Structural Tables

```{r mga1-tables}
build_path_table <- function(boot_sum, group_label, n) {
  df <- as.data.frame(boot_sum$bootstrapped_paths)
  df$Path <- rownames(df)
  df_tol <- df %>%
    filter(grepl("->  Tolerance", Path)) %>%
    mutate(
      From      = str_replace(Path, "  ->  Tolerance", ""),
      Original  = round(`Original Est.`, 3),
      MeanBoot  = round(`Bootstrap Mean`, 3),
      StdError  = round(`Bootstrap SD`, 3),
      CI_low    = round(`2.5% CI`, 3),
      CI_high   = round(`97.5% CI`, 3),
      T_val     = round(`T Stat.`, 3),
      P_val     = `Bootstrap P Val`,
      Sig       = case_when(
        P_val < 0.001 ~ paste0(T_val, "***"),
        P_val < 0.01  ~ paste0(T_val, "**"),
        P_val < 0.05  ~ paste0(T_val, "*"),
        TRUE          ~ as.character(T_val)
      ),
      Significant = P_val < 0.05
    ) %>%
    select(From, Original, MeanBoot, StdError, CI_low, CI_high, Sig, Significant)

  df_tol %>%
    select(-Significant) %>%
    rename("From" = From, "Original" = Original, "Mean.Boot" = MeanBoot,
           "Std.Error" = StdError, "2.5% CI" = CI_low,
           "97.5% CI"  = CI_high, "T value" = Sig) %>%
    kable(align = "lrrrrrr",
          caption = paste0(group_label, " (n=", n, ") — Paths → Tolerance")) %>%
    kable_styling(font_size = 11, full_width = TRUE,
                  bootstrap_options = c("bordered","condensed")) %>%
    row_spec(0, bold = TRUE, background = "#C6EFCE", color = "black") %>%
    row_spec(which( df_tol$Significant), background = "#FCE4D6", bold = TRUE) %>%
    row_spec(which(!df_tol$Significant), background = "white") %>%
    column_spec(1, bold = TRUE, width = "5cm") %>%
    column_spec(7, bold = TRUE,
                color = ifelse(df_tol$Significant, "#c0392b", "black"))
}

build_path_table(boot_comp_sum,  "With Compensation",    n_comp)
build_path_table(boot_nocomp_sum,"Without Compensation", n_nocomp)
```


## MGA 2 (Parsimonious — No Socio) — Structural Tables

```{r mga2-tables}
build_path_table(boot_comp_sum2,  "With Compensation — No Socio Controls",    n_comp)
build_path_table(boot_nocomp_sum2,"Without Compensation — No Socio Controls", n_nocomp)
```


## Path Coefficients → Tolerance: MGA 1 (Full Model)

```{r mga1-barplot, fig.height=5.5}
ggplot(plot_df, aes(x = reorder(Predictor, abs(Beta)), y = Beta, fill = Group)) +
  geom_col(position = position_dodge(0.7), width = 0.65) +
  geom_hline(yintercept = 0, color = "grey40", linewidth = 0.6) +
  scale_fill_manual(values = c("With Compensation" = "#4a7ab5",
                                "Without Compensation" = "#c0392b")) +
  coord_flip() +
  labs(title    = "MGA 1 (Full): Path Coefficients → Tolerance",
       subtitle = paste0("With compensation: n = ", n_comp,
                         "  |  Without: n = ", n_nocomp),
       x = NULL, y = "Path Coefficient (β)", fill = NULL) +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 13),
        plot.subtitle = element_text(color = "grey40"),
        legend.position = "bottom", panel.grid.minor = element_blank())
```


## Path Coefficients → Tolerance: MGA 2 (No Socio)

```{r mga2-barplot, fig.height=5}
ggplot(plot_df2, aes(x = reorder(Predictor, abs(Beta)), y = Beta, fill = Group)) +
  geom_col(position = position_dodge(0.7), width = 0.65) +
  geom_hline(yintercept = 0, color = "grey40", linewidth = 0.6) +
  scale_fill_manual(values = c("With Compensation" = "#4a7ab5",
                                "Without Compensation" = "#c0392b")) +
  coord_flip() +
  labs(title    = "MGA 2 (No Socio): Path Coefficients → Tolerance",
       subtitle = "Parsimonious specification — socio-demographic controls excluded",
       x = NULL, y = "Path Coefficient (β)", fill = NULL) +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 13),
        plot.subtitle = element_text(color = "grey40"),
        legend.position = "bottom", panel.grid.minor = element_blank())
```


## Bootstrap CIs: MGA 1 (Full Model)

```{r ci-plot1, fig.height=5.5}
ggplot(ci_df, aes(x = Beta, y = reorder(Predictor, abs(Beta)), color = Group)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50", linewidth = 0.7) +
  geom_errorbar(aes(xmin = Lower, xmax = Upper),
                width = 0.3, linewidth = 0.8,
                position = position_dodge(0.5), orientation = "y") +
  geom_point(size = 3, position = position_dodge(0.5)) +
  scale_color_manual(values = c("With Compensation" = "#4a7ab5",
                                 "Without Compensation" = "#c0392b")) +
  labs(title    = "MGA 1 (Full): Bootstrap CIs → Tolerance",
       subtitle = "Overlapping CIs indicate no significant group difference",
       x = "Path Coefficient (β)", y = NULL, color = NULL) +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 13),
        plot.subtitle = element_text(color = "grey40"),
        legend.position = "bottom", panel.grid.minor = element_blank())
```


## Bootstrap CIs: MGA 2 (No Socio)

```{r ci-plot2, fig.height=4.5}
ggplot(ci_df2, aes(x = Beta, y = reorder(Predictor, abs(Beta)), color = Group)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50", linewidth = 0.7) +
  geom_errorbar(aes(xmin = Lower, xmax = Upper),
                width = 0.3, linewidth = 0.8,
                position = position_dodge(0.5), orientation = "y") +
  geom_point(size = 3, position = position_dodge(0.5)) +
  scale_color_manual(values = c("With Compensation" = "#4a7ab5",
                                 "Without Compensation" = "#c0392b")) +
  labs(title    = "MGA 2 (No Socio): Bootstrap CIs → Tolerance",
       subtitle = "Parsimonious specification — core structural paths only",
       x = "Path Coefficient (β)", y = NULL, color = NULL) +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 13),
        plot.subtitle = element_text(color = "grey40"),
        legend.position = "bottom", panel.grid.minor = element_blank())
```


## Permutation Test: MGA 1 (Full Model)

```{r mga1-perm-table}
mga_df %>%
  mutate(Predictor = str_replace_all(Predictor, "_", " ")) %>%
  rename("β With Comp."     = Beta_comp,
         "β Without Comp."  = Beta_nocomp,
         "Δβ"               = Delta,
         "p-value"          = p_value,
         "Sig."             = Significant) %>%
  kable(align = "lrrrrr", booktabs = TRUE) %>%
  kable_styling(font_size = 11, full_width = TRUE,
                bootstrap_options = c("bordered","condensed")) %>%
  row_spec(0, bold = TRUE, background = "#C6EFCE", color = "black") %>%
  row_spec(which(mga_df$Significant == "Yes *"), background = "#FCE4D6", bold = TRUE) %>%
  row_spec(which(mga_df$Significant == "No"),    background = "white") %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(5, color = ifelse(mga_df$p_value < 0.05, "#c0392b", "black"),
              bold  = ifelse(mga_df$p_value < 0.05, TRUE, FALSE))
```


## Permutation Test: MGA 2 (No Socio)

```{r mga2-perm-table}
mga_df2 %>%
  mutate(Predictor = str_replace_all(Predictor, "_", " ")) %>%
  rename("β With Comp."     = Beta_comp,
         "β Without Comp."  = Beta_nocomp,
         "Δβ"               = Delta,
         "p-value"          = p_value,
         "Sig."             = Significant) %>%
  kable(align = "lrrrrr", booktabs = TRUE) %>%
  kable_styling(font_size = 11, full_width = TRUE,
                bootstrap_options = c("bordered","condensed")) %>%
  row_spec(0, bold = TRUE, background = "#C6EFCE", color = "black") %>%
  row_spec(which(mga_df2$Significant == "Yes *"), background = "#FCE4D6", bold = TRUE) %>%
  row_spec(which(mga_df2$Significant == "No"),    background = "white") %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(5, color = ifelse(mga_df2$p_value < 0.05, "#c0392b", "black"),
              bold  = ifelse(mga_df2$p_value < 0.05, TRUE, FALSE))
```


## R² per Group

```{r r2-mga-table}
data.frame(
  Model = c("MGA 1 — Full Model", "MGA 1 — Full Model",
            "MGA 2 — No Socio",   "MGA 2 — No Socio"),
  Group = c("With Compensation (n=277)","Without Compensation (n=348)",
            "With Compensation (n=277)","Without Compensation (n=348)"),
  R2    = round(c(
    pls_comp$rSquared["Rsq",    "Tolerance"],
    pls_nocomp$rSquared["Rsq",  "Tolerance"],
    pls_comp2$rSquared["Rsq",   "Tolerance"],
    pls_nocomp2$rSquared["Rsq", "Tolerance"]
  ), 3),
  AdjR2 = round(c(
    pls_comp$rSquared["AdjRsq",    "Tolerance"],
    pls_nocomp$rSquared["AdjRsq",  "Tolerance"],
    pls_comp2$rSquared["AdjRsq",   "Tolerance"],
    pls_nocomp2$rSquared["AdjRsq", "Tolerance"]
  ), 3)
) %>%
  rename("Model Version" = Model, "Group" = Group, "R²" = R2, "Adj. R²" = AdjR2) %>%
  kable(align = "llrr", booktabs = TRUE) %>%
  kable_styling(font_size = 12, full_width = FALSE,
                bootstrap_options = c("bordered","condensed")) %>%
  row_spec(0, bold = TRUE, background = "#C6EFCE", color = "black") %>%
  row_spec(c(1,3), background = "#dce9f7") %>%
  row_spec(c(2,4), background = "#fde8e8") %>%
  column_spec(2, bold = TRUE)
```


## Section 3.4 Key Takeaways

**Result: Structural relationships are largely invariant across groups**

- **MGA 1 (Full):** Only HouseholdAsset shows a significant group difference (p = 0.003) — all core paths are invariant
- **MGA 2 (No Socio):** Confirms the same finding without demographic controls — group invariance holds in the parsimonious specification too
- Intangible Costs → Tolerance is **significant in both groups** across both MGA versions
- Results are consistent regardless of whether socio-demographic controls are included

> **Interpretation:** A permutation-based MGA (*n* = 1,000 permutations) was conducted in two specifications. Both confirm structural invariance across the compensation and non-compensation groups (all core paths p > .05). The finding that intangible costs are the dominant predictor of tolerance is robust across groups and model specifications.
