---
title: "Consulting Project"
subtitle: "The Compensation Paradox: A PLS-SEM Approach"
author: "Duc-Anh Nguyen"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(readxl)
library(seminr)
library(dplyr)
library(glmnet)
library(rsvg)
# install.packages("rsvg")
```

## Introduction:
This analysis (first edition) tries to answer the following questions and also to leverage all of our modeling choices:

### Research Questions:
1. Does compensation for wild boar damage have a direct effect on tolerance toward wild boar, or is its influence mediated by other social and psychological factors? 
2. What roles do tangible costs, intangible costs, and intangible benefits play in shaping tolerance, and how do these factors interact with compensation experience? 



### Methodological Challenges:
1. Model performance and specification 
  a. How can the structural model be improved (e.g. path structure, mediation, moderation)?  
  b. Should certain constructs be merged, re-specified, or modeled formatively vs. reflectively? 
2. Measurement model refinement 
  a. Assessment and improvement of construct validity and reliability 
  b. Evaluation of indicator selection and potential redundancy 



## Main analysis

### Data Prep

```{r dataPrep}
# Load the dataset
## Data_all---------
# Input data
Data_all <- read_excel("../data/3_Data.xlsx")

head(Data_all)
colnames(Data_all)

# Model Data Selection
Data_allinput <- Data_all %>%
  select("CP_WB1", "CP_WB2", "CP_WB3", "CP_WB4","CP_A1", "CP_A2", "CP_A3",
         "TC1_DamagedArea", "TC2_EconomicLoss", "IC1",
         "IC2_1","IC2_2","IC2_3","IC2_DescriptiveAttitude",
         "IB", "Tol1_5", "Tol2_1", "Tol3_1", "Tol4_5",
         "PE", "CE0","CE1", "CE2", "CA1", "CA2", "CA3", "PS1", "PS2",
         "Q4_Gender","Q5_Age","Q6_Education", "Q8_AnnualIncome",
         "Q14_HouseholdAsset","Q14_CropAsset")

Data_allinput <- Data_allinput %>%
  mutate(across(everything(), ~as.numeric(as.character(.))))

Data_allinput <- scale(Data_allinput)

head(Data_allinput)
```
















# new analysis part
## Model0
```{r model0}
# Load the required library
library(seminr)

# Assuming Data_allinput is already loaded, numeric, and scaled
# Data_allinput <- scale(Data_allinput) %>% as.data.frame()

# -------------------------------------------------------------------
# 1. Define Measurement Model (Outer Model)
# -------------------------------------------------------------------
# In seminr, Mode A (Reflective) uses `reflective()` or `composite()`
# Mode B (Formative) strictly uses `composite(..., weights = mode_B)`

mm_model0 <- constructs(
  # Formative Exogenous
  composite("ConflictExp_WB",            c("CP_WB1", "CP_WB2", "CP_WB3", "CP_WB4"), weights = mode_B),
  composite("ConflictExp_A",             c("CP_A1", "CP_A2", "CP_A3"), weights = mode_B),
  
  # Formative Endogenous (Mitigation)
  composite("Prevention_Effectiveness",  single_item("PE")), # Single items don't need mode_B specified
  composite("Compensation_Experience",   single_item("CE0")),
  composite("Compensation_Anticipation", c("CA1", "CA2", "CA3"), weights = mode_B),
  composite("Policy_Support",            c("PS1", "PS2"), weights = mode_B),
  
  # Formative Endogenous (Costs)
  composite("Tangible_Costs",            c("TC1_DamagedArea", "TC2_EconomicLoss"), weights = mode_B),
  composite("Intangible_Costs",          c("IC1", "IC2_1", "IC2_2", "IC2_3"), weights = mode_B),
  
  # Reflective Endogenous & Controls
  reflective("Intangible_Benefits",      single_item("IB")),
  reflective("Gender",                   single_item("Q4_Gender")),
  reflective("Age",                      single_item("Q5_Age")),
  reflective("Education",                single_item("Q6_Education")),
  reflective("AnnualIncome",             single_item("Q8_AnnualIncome")),
  reflective("HouseholdAsset",           single_item("Q14_CropAsset")),
  reflective("Tolerance",                c("Tol1_5", "Tol2_1", "Tol3_1", "Tol4_5"))
)

# -------------------------------------------------------------------
# 2. Define Structural Model (Inner Model)
# -------------------------------------------------------------------
# Instead of a confusing matrix of 0s and 1s, we literally spell out the causal paths.

sm_model0 <- relationships(
  # Block 1: Conflict Experience predicts Mitigation & Policy
  paths(from = c("ConflictExp_WB", "ConflictExp_A"), 
        to   = c("Prevention_Effectiveness", "Compensation_Experience", "Compensation_Anticipation", "Policy_Support")),
  
  # Block 2: Conflict + Mitigation predicts Costs & Benefits
  paths(from = c("ConflictExp_WB", "ConflictExp_A", "Prevention_Effectiveness", "Compensation_Experience", "Compensation_Anticipation", "Policy_Support"), 
        to   = c("Tangible_Costs", "Intangible_Costs", "Intangible_Benefits")),
  
  # Block 3: EVERYTHING predicts Tolerance
  paths(from = c("ConflictExp_WB", "ConflictExp_A", "Prevention_Effectiveness", 
                 "Compensation_Experience", "Compensation_Anticipation", "Policy_Support", 
                 "Tangible_Costs", "Intangible_Costs", "Intangible_Benefits",
                 "Gender", "Age", "Education", "AnnualIncome", "HouseholdAsset"), 
        to   = "Tolerance")
)

# -------------------------------------------------------------------
# 3. Estimate the PLS Model
# -------------------------------------------------------------------
pls_model0 <- estimate_pls(data = Data_allinput, 
                           measurement_model = mm_model0, 
                           structural_model = sm_model0,
                           inner_weights = path_weighting)

# -------------------------------------------------------------------
# 4. Bootstrap for Significance (p-values & t-values)
# -------------------------------------------------------------------
set.seed(123) # For reproducibility
boot_model0 <- bootstrap_model(pls_model0, nboot = 500)












# -------------------------------------------------------------------
# 5. Review Results
# -------------------------------------------------------------------
summary_pls0  <- summary(pls_model0)
summary_boot0 <- summary(boot_model0)

# 1. R-Squared and Path Coefficients
cat("\n--- Structural Paths & R-Squared ---\n")
print(summary_pls0$paths)

# 2. Significance of the paths (t-values and p-values)
cat("\n--- Bootstrapped Path Significance ---\n")
print(summary_boot0$bootstrapped_paths)


# 3. 
cat("\n--- Formative Indicators ---\n")
print(summary_boot0$bootstrapped_weights)


cat("\n--- Reflective Indicators ---\n")
print(summary_boot0$bootstrapped_loadings)

# 4. VIFs for Formative Indicators
cat("\n--- Variance Inflation Factors (VIF) ---\n")
print(summary_pls0$validity$vif_items)
```



#### Model 0.1
Dropped: CP_WB3, CA1, CA2, IC2_3, Tol3_1
```{r model0.1}
library(seminr)

# Ensure data is a standard data frame
df <- as.data.frame(Data_allinput)

# -------------------------------------------------------------------
# 1. Define Measurement Model 0.1
# -------------------------------------------------------------------
mm_0_1 <- constructs(
  # Formative Exogenous
  composite("ConflictExp_WB",            c("CP_WB1", "CP_WB2", "CP_WB4"), weights = mode_B),
  composite("ConflictExp_A",             c("CP_A1", "CP_A2", "CP_A3"), weights = mode_B),
  
  # Single Items (Mode doesn't matter, but classified as composite/reflective for consistency)
  composite("Prevention_Effectiveness",  single_item("PE")),
  composite("Compensation_Experience",   single_item("CE0")),
  composite("Compensation_Anticipation", single_item("CA3")), # CA1 and CA2 dropped
  
  # Formative Endogenous
  composite("Policy_Support",            c("PS1", "PS2"), weights = mode_B),
  composite("Tangible_Costs",            c("TC1_DamagedArea", "TC2_EconomicLoss"), weights = mode_B),
  composite("Intangible_Costs",          c("IC1", "IC2_1", "IC2_2"), weights = mode_B), # IC2_3 dropped
  
  # Reflective Endogenous & Single Item Controls
  reflective("Intangible_Benefits",      single_item("IB")),
  reflective("Gender",                   single_item("Q4_Gender")),
  reflective("Age",                      single_item("Q5_Age")),
  reflective("Education",                single_item("Q6_Education")),
  reflective("AnnualIncome",             single_item("Q8_AnnualIncome")),
  reflective("HouseholdAsset",           single_item("Q14_CropAsset")),
  reflective("Tolerance",                c("Tol1_5", "Tol2_1", "Tol4_5")) # Tol3_1 dropped
)

# -------------------------------------------------------------------
# 2. Define Structural Model (Same for all Model 0 iterations)
# -------------------------------------------------------------------
sm_baseline <- relationships(
  paths(from = c("ConflictExp_WB", "ConflictExp_A"), 
        to   = c("Prevention_Effectiveness", "Compensation_Experience", "Compensation_Anticipation", "Policy_Support")),
  
  paths(from = c("ConflictExp_WB", "ConflictExp_A", "Prevention_Effectiveness", "Compensation_Experience", "Compensation_Anticipation", "Policy_Support"), 
        to   = c("Tangible_Costs", "Intangible_Costs", "Intangible_Benefits")),
  
  paths(from = c("ConflictExp_WB", "ConflictExp_A", "Prevention_Effectiveness", 
                 "Compensation_Experience", "Compensation_Anticipation", "Policy_Support", 
                 "Tangible_Costs", "Intangible_Costs", "Intangible_Benefits",
                 "Gender", "Age", "Education", "AnnualIncome", "HouseholdAsset"), 
        to   = "Tolerance")
)

# -------------------------------------------------------------------
# 3. Estimate and Bootstrap Model 0.1
# -------------------------------------------------------------------
pls_0_1 <- estimate_pls(data = df, measurement_model = mm_0_1, structural_model = sm_baseline)
set.seed(123)
boot_0_1 <- bootstrap_model(pls_0_1, nboot = 500)

sum_0_1 <- summary(pls_0_1)
sum_boot_0_1 <- summary(boot_0_1)


# 1. R-Squared and Path Coefficients
cat("\n--- Structural Paths & R-Squared ---\n")
print(sum_0_1$paths)

# 2. Significance of the paths (t-values and p-values)
cat("\n--- Bootstrapped Path Significance ---\n")
print(sum_boot_0_1$bootstrapped_paths)


# 3. 
cat("\n--- Formative Indicators ---\n")
print(sum_boot_0_1$bootstrapped_weights)


cat("\n--- Reflective Indicators ---\n")
print(sum_boot_0_1$bootstrapped_loadings)

# 4. VIFs for Formative Indicators
cat("\n--- Variance Inflation Factors (VIF) ---\n")
print(sum_0_1$validity$vif_items)
```






## model 0.2
Further Dropped: CP_A3, IC2_1, IC2_2
```{r model0.2}

# -------------------------------------------------------------------
# 1. Define Measurement Model 0.2
# -------------------------------------------------------------------
mm_0_2 <- constructs(
  composite("ConflictExp_WB",            c("CP_WB1", "CP_WB2", "CP_WB4"), weights = mode_B),
  composite("ConflictExp_A",             c("CP_A1", "CP_A2"), weights = mode_B), # CP_A3 dropped
  
  composite("Prevention_Effectiveness",  single_item("PE")),
  composite("Compensation_Experience",   single_item("CE0")),
  composite("Compensation_Anticipation", single_item("CA3")), 
  
  composite("Policy_Support",            c("PS1", "PS2"), weights = mode_B),
  composite("Tangible_Costs",            c("TC1_DamagedArea", "TC2_EconomicLoss"), weights = mode_B),
  composite("Intangible_Costs",          single_item("IC1")), # IC2_1 and IC2_2 dropped (Now single item)
  
  reflective("Intangible_Benefits",      single_item("IB")),
  reflective("Gender",                   single_item("Q4_Gender")),
  reflective("Age",                      single_item("Q5_Age")),
  reflective("Education",                single_item("Q6_Education")),
  reflective("AnnualIncome",             single_item("Q8_AnnualIncome")),
  reflective("HouseholdAsset",           single_item("Q14_CropAsset")),
  reflective("Tolerance",                c("Tol1_5", "Tol2_1", "Tol4_5")) 
)

# -------------------------------------------------------------------
# 2. Estimate and Bootstrap Model 0.2
# -------------------------------------------------------------------
pls_0_2 <- estimate_pls(data = df, measurement_model = mm_0_2, structural_model = sm_baseline, inner_weights = path_weighting)
set.seed(123)
boot_0_2 <- bootstrap_model(pls_0_2, nboot = 500)

# Generate Summaries for Evaluation
sum_0_2 <- summary(pls_0_2)
sum_boot_0_2 <- summary(boot_0_2)



# 1. R-Squared and Path Coefficients
cat("\n--- Structural Paths & R-Squared ---\n")
print(sum_0_2$paths)

# 2. Significance of the paths (t-values and p-values)
cat("\n--- Bootstrapped Path Significance ---\n")
print(sum_boot_0_2$bootstrapped_paths)


# 3. 
cat("\n--- Formative Indicators ---\n")
print(sum_boot_0_2$bootstrapped_weights)


cat("\n--- Reflective Indicators ---\n")
print(sum_boot_0_2$bootstrapped_loadings)

# 4. VIFs for Formative Indicators
cat("\n--- Variance Inflation Factors (VIF) ---\n")
print(sum_0_2$validity$vif_items)
```






```{r model0.3}

# -------------------------------------------------------------------
# 1. Define Measurement Model 0.3
# -------------------------------------------------------------------
mm_0_3 <- constructs(
  composite("ConflictExp_WB",            c("CP_WB1", "CP_WB2", "CP_WB4"), weights = mode_B),
  composite("ConflictExp_A",             single_item("CP_A1")), # CP_A2 dropped
  
  composite("Prevention_Effectiveness",  single_item("PE")),
  composite("Compensation_Experience",   single_item("CE0")),
  composite("Compensation_Anticipation", single_item("CA3")), 
  
  composite("Policy_Support",            c("PS1", "PS2"), weights = mode_B),
  composite("Tangible_Costs",            c("TC1_DamagedArea", "TC2_EconomicLoss"), weights = mode_B),
  composite("Intangible_Costs",          single_item("IC1")),
  
  reflective("Intangible_Benefits",      single_item("IB")),
  reflective("Gender",                   single_item("Q4_Gender")),
  reflective("Age",                      single_item("Q5_Age")),
  reflective("Education",                single_item("Q6_Education")),
  reflective("AnnualIncome",             single_item("Q8_AnnualIncome")),
  reflective("HouseholdAsset",           single_item("Q14_CropAsset")),
  reflective("Tolerance",                c("Tol1_5", "Tol2_1", "Tol4_5")) 
)

# -------------------------------------------------------------------
# 2. Estimate and Bootstrap Model 0.3
# ------------------------------------------------------------------
pls_0_3 <- estimate_pls(data = df, measurement_model = mm_0_3, structural_model = sm_baseline, inner_weights = path_weighting)
set.seed(123)
boot_0_3 <- bootstrap_model(pls_0_3, nboot = 500)

# Generate Summaries for Evaluation
sum_0_3 <- summary(pls_0_3)
sum_boot_0_3 <- summary(boot_0_3)



# # 1. R-Squared and Path Coefficients
# cat("\n--- Structural Paths & R-Squared ---\n")
# print(sum_0_3$paths)
# 
# # 2. Significance of the paths (t-values and p-values)
# cat("\n--- Bootstrapped Path Significance ---\n")
# print(sum_boot_0_3$bootstrapped_paths)
# 
# 
# # 3. 
# cat("\n--- Formative Indicators ---\n")
# print(sum_boot_0_3$bootstrapped_weights)
# 
# 
# cat("\n--- Reflective Indicators ---\n")
# print(sum_boot_0_3$bootstrapped_loadings)
# 
# # 4. VIFs for Formative Indicators
# cat("\n--- Variance Inflation Factors (VIF) ---\n")
# print(sum_0_3$validity$vif_items)
```



### Evaluation 0.3
```{r eval}

cat("\n=======================================================\n")
cat("EVALUATION CRITERIA: MEASUREMENT MODEL 0.3\n")
cat("=======================================================\n")

# ---------------------------------------------------------
# 1. Collinearity Check (Outer VIF < 3.3 for Formatives)
# ---------------------------------------------------------
cat("\n[1] OUTER VIFs (Collinearity Check for Formative Constructs)\n")
cat("Target: Values should be < 3.3. Single items will equal 1.\n")
print(sum_0_3$validity$vif_items)

# ---------------------------------------------------------
# 2. Convergent Validity & Internal Consistency (Reflective)
# ---------------------------------------------------------
cat("\n[2] RELIABILITY & CONVERGENT VALIDITY (Reflective Constructs)\n")
cat("Target: AVE >= 0.5, Composite Reliability (rhoC) >= 0.7, Alpha >= 0.7\n")
print(sum_0_3$reliability)

# ---------------------------------------------------------
# 3. Discriminant Validity
# ---------------------------------------------------------
cat("\n[3A] DISCRIMINANT VALIDITY: HTMT (Reflective Constructs)\n")
cat("Target: Values should be < 0.90\n")
print(sum_0_3$validity$htmt)


cat("\n[3B] DISCRIMINANT VALIDITY: Fornell-Larcker (Reflective Constructs)\n")
# Target: The square root of AVE (diagonal) should be > correlations (off-diagonal)
print(sum_0_3$validity$fl_criteria)


cat("\n[3C] DISCRIMINANT VALIDITY: Cross-Loadings\n")
cat("Target: An indicator should load highest on its own construct.\n")
print(sum_0_3$validity$cross_loadings)

# ---------------------------------------------------------
# 4. Significance Testing
# ---------------------------------------------------------
cat("\n[4A] SIGNIFICANCE OF OUTER WEIGHTS (Formative Constructs)\n")
cat("Target: t-value > 1.96 / p-value < 0.05\n")
print(sum_boot_0_3$bootstrapped_weights)

cat("\n[4B] SIGNIFICANCE OF OUTER LOADINGS (Reflective Constructs)\n")
cat("Target: Loading > 0.5, t-value > 1.96 / p-value < 0.05\n")
print(sum_boot_0_3$bootstrapped_loadings)

cat("\n=======================================================\n")
cat("STRUCTURAL MODEL EVALUATION\n")
cat("=======================================================\n")

cat("\n[5] EXPLANATORY POWER (R-Squared)\n")
print(sum_0_3$paths[c("R^2", "AdjR^2"), ])

cat("\n[6] SIGNIFICANCE OF STRUCTURAL PATHS (Inner Model)\n")
print(sum_boot_0_3$bootstrapped_paths)
```































```{r interactions}


# -------------------------------------------------------------------
# Correct Implementation of Interaction in seminr
# -------------------------------------------------------------------

# 1. Define Measurement Model (Interaction MUST be defined here)
mm_interaction <- constructs(
  composite("ConflictExp_WB",            c("CP_WB1", "CP_WB2", "CP_WB4"), weights = mode_B),
  composite("ConflictExp_A",             single_item("CP_A1")), 
  composite("Prevention_Effectiveness",  single_item("PE")),
  composite("Compensation_Experience",   single_item("CE0")),
  composite("Compensation_Anticipation", single_item("CA3")), 
  composite("Policy_Support",            c("PS1", "PS2"), weights = mode_B),
  composite("Tangible_Costs",            c("TC1_DamagedArea", "TC2_EconomicLoss"), weights = mode_B),
  composite("Intangible_Costs",          single_item("IC1")), 
  reflective("Intangible_Benefits",      single_item("IB")),
  reflective("Tolerance",                c("Tol1_5", "Tol2_1", "Tol4_5")),
  
  # DEFINE INTERACTION: iv = Independent Var, moderator = Moderator
  interaction_term(iv = "Intangible_Costs", 
                   moderator = "Compensation_Experience", 
                   method = two_stage)
)

# 2. Define Structural Model (Refer to the interaction by its string name)
# Note: seminr names it "Intangible_Costs*Compensation_Experience"
sm_interaction <- relationships(
  # Predictors of Costs/Benefits
  paths(from = c("ConflictExp_WB", "ConflictExp_A", "Prevention_Effectiveness", 
                 "Compensation_Experience", "Compensation_Anticipation", "Policy_Support"), 
        to   = c("Tangible_Costs", "Intangible_Costs", "Intangible_Benefits")),
  
  # Predictors of Tolerance (Including the Interaction Name as a string)
  paths(from = c("Intangible_Costs", "Compensation_Experience", "Intangible_Benefits", 
                 "Policy_Support", "Tangible_Costs",
                 "Intangible_Costs*Compensation_Experience"), 
        to   = "Tolerance")
)

# 3. Estimate (Crucial: Use mm_interaction here!)
pls_interaction <- estimate_pls(data = df, 
                                measurement_model = mm_interaction, 
                                structural_model = sm_interaction)

# 4. Bootstrap and Summary
boot_interaction <- bootstrap_model(pls_interaction, nboot = 500)
sum_interaction <- summary(pls_interaction)
sum_boot_interaction <- summary(boot_interaction)

# Print results
print(sum_boot_interaction$bootstrapped_paths)
print(sum_interaction$fSquare)


```



```{r EFA}
# -------------------------------------------------------------------
# Exploratory Factor Analysis (EFA) for Discriminant Validity Check
# -------------------------------------------------------------------
library(psych)
library(dplyr)

# 1. Convert matrix to data frame and select columns
# We use dplyr::select to ensure we use the correct function
efa_data <- as.data.frame(Data_allinput) %>%
  dplyr::select(PS1, PS2, IC1, IC2_1, IC2_2, IC2_3)

# 2. Check suitability for Factor Analysis
# KMO should be > 0.6; Bartlett's p < 0.05
print(KMO(efa_data))
print(cortest.bartlett(cor(efa_data), n = nrow(efa_data)))

# 3. Run the EFA (Extracting 2 factors)
# fm = "minres" is standard; rotate = "varimax" helps see clear separation
efa_result <- fa(efa_data, nfactors = 2, rotate = "varimax", fm = "minres")

# 4. Print the factor loadings with a cutoff of 0.3 to see "clean" clusters
print(efa_result$loadings, cutoff = 0.3)

```


Goal: To prove mathematically whether Policy_Support and Intangible_Costs are two distinct psychological concepts, or if respondents blurred them together (which caused the HTMT > 0.90 violation).

Note: To run a CFA, we must use the items from before we deleted them down to single items. We will test a 2-Factor Model against a 1-Factor Model.
```{r CFA}
# library(seminr)
# 
# # Ensure data is a data frame
# df <- as.data.frame(Data_allinput)
# 
# # -------------------------------------------------------------------
# # 1. Define Measurement Models for CFA
# # -------------------------------------------------------------------
# 
# # Model A: The 2-Factor Theory (They are distinct)
# cfa_mm_2f <- constructs(
#   reflective("Policy_Support", c("PS1", "PS2")),
#   reflective("Intangible_Costs", c("IC1", "IC2_1", "IC2_2"))
# )
# 
# # Model B: The 1-Factor Theory (They are blurred together)
# cfa_mm_1f <- constructs(
#   reflective("Blurred_Construct", c("PS1", "PS2", "IC1", "IC2_1", "IC2_2"))
# )
# 
# # -------------------------------------------------------------------
# # 2. Estimate the CFA Models
# # -------------------------------------------------------------------
# # Instead of estimate_pls(), we use estimate_cfa()
# cfa_2f <- estimate_cfa(data = df, measurement_model = cfa_mm_2f, check.gradient = FALSE)
# cfa_1f <- estimate_cfa(data = df, measurement_model = cfa_mm_1f, check.gradient = FALSE)
# 
# # -------------------------------------------------------------------
# # 3. Review and Compare Results
# # -------------------------------------------------------------------
# 
# # Print standard CFA fit metrics (CFI, RMSEA, SRMR) for the 2-factor model
# summary_cfa_2f <- summary(cfa_2f)
# cat("\n--- CFA 2-Factor Fit Metrics ---\n")
# print(summary_cfa_2f$quality$fit)
# 
# # Compare the two models to see which fits the data better.
# # Because seminr uses lavaan under the hood, we can extract the base 
# # lavaan models and run a standard Chi-Square Difference Test (ANOVA).
# cat("\n--- CFA Model Comparison (2-Factor vs 1-Factor) ---\n")
# anova_result <- anova(cfa_1f$lavaan_model, cfa_2f$lavaan_model)
# print(anova_result)
# 
# 
# inspect(cfa_2f$lavaan_model, "cor.lv")

```
The optimizer is saying it "converged" (found a result) but the gradient is not zero: the math is unstable because the two factors you are trying to separate (Policy_Support and Intangible_Costs) are so highly correlated that the software can't find a unique peak for each. They are essentially a single flat "plateau" in the mathematical space.

This happens in CFA when:
+ Constructs are redundant: They are 95%+ the same thing.
+ Too few indicators: Policy_Support only has 2 items. In Covariance-Based SEM (CFA), a 2-item factor is often "under-identified" and unstable unless it correlates strongly with other things.

To investigate the high HTMT value (1.112) between Policy Support and Intangible Costs, we attempted a Confirmatory Factor Analysis. The model initially struggled to converge because the mathematical gradient was unstable. This provides objective evidence that these two constructs share a very high degree of common variance in the residents' minds.


```{r visualisation}
# -------------------------------------------------------------------
# Visualising Models using seminr
# -------------------------------------------------------------------

# 1. Plot Model 0 (The Kitchen Sink Baseline)
# This will show all 34 indicators and the structural paths
plot_m0 <- plot(pls_model0, title = "Model 0: Baseline Measurement Model")
plot_m0
# 
# # 2. Plot Model 0.1 (Intermediate Cleanup)
plot_m0_1 <- plot(pls_0_1, title = "Model 0.1: Refined Measurement Model")
plot_m0_1

# 3. Plot Model 0.2 (Strict Parsimony - Final Model)
plot_m0_2 <- plot(pls_0_2, title = "Model 0.2: Final Parsimonious Model")
plot_m0_2


# This is the cleanest model, perfectly suited for your main presentation slide
plot_m0_3 <- plot(pls_0_3, title = "Model 0.3: Final Parsimonious Model")
plot_m0_3


# -------------------------------------------------------------------
# Exporting Plots for the Final Presentation
# -------------------------------------------------------------------

# Save as PDF (Best for keeping text sharp if you need to zoom in)
save_plot("Model_0_Baseline.pdf", plot_m0)
save_plot("Model_0_1_Intermediate.pdf", plot_m0_1)
save_plot("Model_0_2_Final.pdf", plot_m0_2)
save_plot("Model_0_3_Final.pdf", plot_m0_3)


```


```{r visualisation2}


# Define a theme that hides specific paths (e.g., from demographics)
# This keeps the latent variables in the plot but makes the lines invisible
# or you can simply omit them from the structural model during the final plot-only run

# Create a 'Plot-Only' structural model without demographics
sm_plot <- relationships(
  paths(from = c("ConflictExp_WB", "ConflictExp_A", "Prevention_Effectiveness", 
                 "Compensation_Experience", "Compensation_Anticipation", "Policy_Support"), 
        to   = c("Tangible_Costs", "Intangible_Costs", "Intangible_Benefits")),
  
  paths(from = c("Intangible_Costs", "Compensation_Experience", "Intangible_Benefits", 
                 "Policy_Support", "Tangible_Costs", "Prevention_Effectiveness"), 
        to   = "Tolerance")
)

# Estimate a temporary model JUST for the diagram
pls_plot_only <- estimate_pls(data = df, 
                              measurement_model = mm_0_3, 
                              structural_model = sm_plot)

# Plot it
plot_final <- plot(pls_plot_only, title = "Model 0.3: Key Drivers of Tolerance")

save_plot("Model_0.3_Final.pdf", plot_final)


```






