---
title: "Consulting Project"
subtitle: "The Compensation Paradox: A PLS-SEM Approach"
author: "Duc-Anh Nguyen, Vaishali Iyer, Jihao Li"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(readxl)
library(seminr)
library(dplyr)
library(glmnet)
```


### 1 Data Prep

```{r dataPrep}
# Load the dataset
df <- read_excel("../data/3_Data.xlsx")
df <- as.data.frame(df) # Ensure standard dataframe format for seminr

# Standardize the large financial variable to prevent convergence issues
df$TC2_EconomicLoss_Std <- scale(df$TC2_EconomicLoss)
```


### measurement model evaluation (challenges 1b,2a,2b)
1b and 2b: model intangible costs and policy support as formative constructs to retained nuanced survey items without relying on reflective correlations.

Redundant/ non significant indicators Tol3, CA1, CA2 are removed


2a: evaluate Contruct Validity AVE and discriminant validity HTMT
```{r 1b2a2b}
# Define the base measurement model (including the interaction term for later)
mm_base <- constructs(
  reflective("Tolerance",          multi_items("Tol", c("1_5", "2_1", "4_5"))),
  composite("Intangible_Cost",     multi_items("IC", c("1", "2_1", "2_2", "2_3")), weights = mode_B),
  composite("Policy_Support",      multi_items("PS", c("1", "2")), weights = mode_B),
  composite("Intangible_Benefit",  single_item("IB")),
  composite("Tangible_Cost",       single_item("TC2_EconomicLoss_Std")),
  composite("Compensation",        single_item("CE0")),
  
  # Prepare for RQ2 Moderation:
  interaction_term(iv = "Compensation", moderator = "Intangible_Cost", method = two_stage)
)

# Define a simple structural model just to extract measurement validity
sm_simple <- relationships(
  paths(from = c("Compensation", "Intangible_Cost", "Policy_Support", "Intangible_Benefit", "Tangible_Cost"), 
        to = "Tolerance")
)

# Estimate base model
pls_model_base <- estimate_pls(data = df, measurement_model = mm_base, structural_model = sm_simple)
summary_base <- summary(pls_model_base)

print("=== Construct Reliability & Validity (Challenge 2a) ===")
summary_base$reliability

print("=== Discriminant Validity HTMT (Challenge 2a) ===")
summary_base$validity$htmt

```



### RQ1: direct and meidated effects
testing the specific indirect pathway: conpensation -> intangible costs -> tolerance
```{r }
# Define structural model for mediation
sm_mediation <- relationships(
  paths(from = "Compensation", to = c("Intangible_Cost", "Policy_Support", "Tolerance")),
  paths(from = c("Intangible_Cost", "Policy_Support", "Intangible_Benefit", "Tangible_Cost"), 
        to = "Tolerance")
)

pls_model_med <- estimate_pls(data = df, measurement_model = mm_base, structural_model = sm_mediation)
set.seed(123)
boot_model_med <- bootstrap_model(seminr_model = pls_model_med, nboot = 5000)

print("=== RQ1: Direct Structural Paths ===")
summary(boot_model_med)$bootstrapped_paths

print("=== RQ1: Bootstrapped Mediation (Compensation -> Intangible Cost -> Tolerance) ===")
specific_effect_significance(boot_model_med, 
                             from = "Compensation", 
                             through = "Intangible_Cost", 
                             to = "Tolerance",
                             alpha = 0.05)

```



### RQ2 and 1a: moderation and role of costs/enefits
RQ2: do (in)tangible costs interact with compensation experience?

1a: improve the structural model by adding the interaction term compensation x Intangible_cost
```{r }
# Define the Structural Model WITH Moderation
sm_moderation <- relationships(
  paths(from = c("Compensation", "Intangible_Cost", "Intangible_Benefit", "Policy_Support"), 
        to = "Tolerance"),
  paths(from = "Compensation", to = c("Intangible_Cost", "Policy_Support")),
  
  # THE MODERATION PATH
  paths(from = "Compensation*Intangible_Cost", to = "Tolerance")
)

# Estimate and Bootstrap the new model using path_weighting for interactions
pls_model_mod <- estimate_pls(data = df, 
                              measurement_model = mm_base, 
                              structural_model = sm_moderation,
                              inner_weights = path_weighting)

boot_model_mod <- bootstrap_model(pls_model_mod, nboot = 5000)

print("=== RQ2: FINAL MODERATION RESULTS ===")
summary(boot_model_mod)$bootstrapped_paths

```


### 3a: model evaluation metrics


```{r }

summary_mod <- summary(pls_model_mod)

print("=== Effect Sizes f^2 (Challenge 3a) ===")
# f^2 > 0.02 is small, > 0.15 is medium, > 0.35 is large
summary_mod$fSquare

print("=== Model Fit SRMR (Challenge 3a) ===")
# Safe extraction for two-stage moderation models
qc <- summary_mod$quality_criteria
if (!is.null(qc$fit$srmr)) {
  cat("Model Fit (SRMR):", round(qc$fit$srmr, 4), "\n")
} else {
  cat("Note: Global SRMR aggregation not available for this two-stage model.\n")
}

print("=== Predictive Relevance Q^2 (Challenge 3a) ===")
# Forced to 1 core to prevent parallelization 'cl' error
predict_results <- predict_pls(pls_model_mod, noFolds = 10, cores = 1) 
print(summary(predict_results))
```


### RQ3 & Challenge 3b: 
A formal multi-group analysis (MGA) to test whether differences between the compensation and non-compensation groups are statistically significant.
```{r }
# Define a Structural model for MGA (Compensation is the grouping variable, so it is removed from the model)
mm_mga <- constructs(
  reflective("Tolerance", multi_items("Tol", c("1_5", "2_1", "4_5"))),
  composite("Intangible_Cost", multi_items("IC", c("1", "2_1", "2_2", "2_3")), weights = mode_B),
  composite("Policy_Support", multi_items("PS", c("1", "2")), weights = mode_B),
  composite("Intangible_Benefit", single_item("IB")),
  composite("Tangible_Cost", single_item("TC2_EconomicLoss_Std"))
)

sm_mga <- relationships(
  paths(from = c("Intangible_Cost", "Policy_Support", "Intangible_Benefit", "Tangible_Cost"), 
        to = "Tolerance")
)

pls_model_mga <- estimate_pls(data = df, measurement_model = mm_mga, structural_model = sm_mga)

# Run the MGA
mga_results <- estimate_pls_mga(pls_model_mga, condition = df$CE0 == 1, nboot = 5000)

print("=== RQ3: Multi-Group Analysis Results ===")
summary(mga_results)

```

### Robustness: Double Machine Learning (DML)
Further addressing RQ3, we use Neyman-Orthogonal scores via LASSO to control for high-dimensional demographic and agricultural confounders.

```{r }
# Create single Tolerance vector
df$Tolerance_Score <- rowMeans(df[, c("Tol1_5", "Tol2_1", "Tol4_5")], na.rm = TRUE)

Y_dml <- df$Tolerance_Score
D_dml <- df$CE0

covariates <- df %>% 
  select(Q4_Gender, Q5_Age, Q6_Education, Q7_HouseholdPop, Q8_AnnualIncome, 
         Q9_AgriProportion, Q11_TotalArea, Q13_TotalLivestock, 
         Q14_CropAsset, Q14_LivestockAsset, TC2_EconomicLoss_Std)

X_dml <- model.matrix(~ .^2, data = covariates)
idx_control <- which(D_dml == 0)
idx_treated <- which(D_dml == 1)

set.seed(123)
lasso_mu0 <- cv.glmnet(X_dml[idx_control, ], Y_dml[idx_control], alpha = 1)
mu0hat <- predict(lasso_mu0, s = "lambda.min", newx = X_dml)

lasso_mu1 <- cv.glmnet(X_dml[idx_treated, ], Y_dml[idx_treated], alpha = 1)
mu1hat <- predict(lasso_mu1, s = "lambda.min", newx = X_dml)

lasso_p <- cv.glmnet(X_dml, D_dml, family = "binomial", alpha = 1)
Phat <- predict(lasso_p, s = "lambda.min", newx = X_dml, type = "response")
Phat <- pmax(pmin(Phat, 0.99), 0.01)

ATE_scores <- (mu1hat - mu0hat) + 
              (D_dml * (Y_dml - mu1hat) / Phat) - 
              ((1 - D_dml) * (Y_dml - mu0hat) / (1 - Phat))

ATE_estimate <- mean(ATE_scores)
ATE_se <- sd(ATE_scores) / sqrt(length(ATE_scores))
t_stat <- ATE_estimate / ATE_se
p_val <- 2 * (1 - pnorm(abs(t_stat)))

print("=== Double Machine Learning (DML) Robustness Check ===")
cat("ATE of Compensation on Tolerance:", round(ATE_estimate, 4), "\n")
cat("P-value:", round(p_val, 4), "\n")

```



```{r }


```



```{r }


```


